SoK: The Evolution of Web Application Attack Defenses

### 2014-10-22 docs/questioning.tex
describing ISR and implementations

{\sc isr} is a method that contrary to the previous
two approaches, has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.

>>>>

{\sc isr} is a method that contrary to the previous
two, has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.
The main idea behind the method, is to
separate code from data by randomizing the legitimate code's 
execution environment. In this way, the malicious code
injected by the attackers who do not know the randomization
algorithm, will not get executed.

{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
to detect {\sc sql} injections in the following manner:
initially, it allows programmers to create {\sc sql} statements
using randomized instructions instead of standard keywords.
The modified queries are either reconstructed at runtime using
the same key that is inaccessible to the malicious user,
or the user input is tagged with delimiters that allow
an augmented {\sc sql} grammar to detect the
attack.

In the case of {\sc xss} attacks that are based on JavaScript,
consider a {\sc xor} function that encodes all JavaScript source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again.
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
